---
title: "Getting started with lpari"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with lpari}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`lpari` implements LPA-RI, a recovery-calibrated index for choosing the number
of profiles in latent profile analysis.

## Old Faithful

Old Faithful is the primary package example because the eruption duration and
waiting-time variables have a clear bimodal structure.

```{r faithful-example, eval = FALSE}
library(lpari)

ex <- load_lpari_example("old_faithful")

fit <- fit_lpari(
  ex$data[, ex$indicators],
  k = 1:5,
  n_starts = 50,
  id = ex$data[[ex$id]],
  seed = 20260525
)

fit
fit$selection
fit$posterior

plot_lpari_posterior(fit)
plot_lpari_profiles(fit)
```

## Supplementary examples

Iris and Holzinger-Swineford are useful for demonstrating the API, but their
external labels should not be treated as guaranteed latent-profile ground truth.

```{r supplementary-examples, eval = FALSE}
iris_fit <- lpari_example("iris", n_starts = 25)
hs_fit <- lpari_example("holzinger_swineford", n_starts = 25)

iris_fit$selection
hs_fit$selection
```

## Reading the posterior-style output

The `posterior_k` column is a calibrated plausibility distribution over the
candidate K values that were actually fitted. It is useful for reporting
enumeration uncertainty, but it is not a generative Bayesian posterior.
